Constructing the transition graphs of interacting hysterons

### 2022-05-30 Paper_draft.tex
Added piece about garden-of-Eden states

>>>>

It often occurs that one or more of the possible states for $N$ hysterons cannot be reached from the ground state. We refer to such states which cannot be reached as garden-of-Eden states. Because the transitions from garden-of-Eden states are irrelevant when one starts from the ground state, as is generally the case in our experiments, we may choose to ignore garden-of-Eden states. As a consequence, when two graphs only differ from one another by transitions that occur from garden-of-Eden states, the graphs become duplicates. Thus, when garden-of-Eden states are ignored, the number of distinct graphs can turn out lower than the number of possible combinations of transitions. 
